\documentclass[10pt]{article}

%% PACKAGES %%

\usepackage[english]{babel} % multilingual support
\usepackage[utf8x]{inputenc} % encoding
\usepackage{blindtext} % to insert blind text
\usepackage{hyperref}
\usepackage[compact]{titlesec}         % you need this package

% Set the default font
\usepackage{tgpagella}

% set the page layout
\usepackage{geometry}
\geometry {
  a4paper,
  left=5mm,
  right=5mm,
  bottom=3mm,
  top=4mm }

% empty the headers, footers, page numbers…
\pagestyle{empty}

% Custom sectioning with secsty
\usepackage{sectsty}

\sectionfont{%                        
    \large % make sections smaller
    \fontfamily{qag}\selectfont % change font family
    \sectionrule{0pt}{0pt}{-5pt}{1pt} % insert a thin rule
}

\titlespacing{\section}{0pt}{0pt}{0pt}

%% MACROS %%

% size of the boxes used to align text
\newlength{\spacebox}
\settowidth{\spacebox}{123456789}

% vertical space separator between entries
\newcommand{\sepspace}{\vspace*{0.1em}}

% name
\newcommand{\name}[1]{
\Huge % font size
\fontfamily{phv}\selectfont % font family
% print name centered and bold
\begin{center} \textbf{#1} \end{center}\par
% back to normal size and font
\normalsize\normalfont}

% motto
\newcommand{\motto}[1]{
  \large % font size
  \fontfamily{phv}\selectfont % font family
% print motto centered and slanted
  \begin{center} \textsl{#1}\end{center}\par
% back to normal size and font
  \normalsize \normalfont}


% personal information
\newcommand{\info}[2]{
% set specific indentation for personal information
  \noindent\hangindent=0em\hangafter=0
% create a box to align two pieces of text
  \parbox{\spacebox}{%
  \textit{#1}} % slanted entry name
  #2 \par} % entry value


% skill
\newcommand{\skill}[2]{
% set specific indentation for personal information
\noindent\hangindent=0em\hangafter=0
% create a box to align two pieces of text
\parbox{3\spacebox}{% three times larger box
\textsc{#1}} % small caps entry name
#2 \par} % entry value

% language level
\newcommand{\lan}[2]{
    % set specific indentation for personal information
    \noindent\hangindent=0em\hangafter=0
    % create a box to align two pieces of text
    \parbox{3\spacebox}{%
        \textbf{#1}} % bold font entry name
     #2 \par}    % entry value

% education entry
\newcommand{\education}[4]{

% name of the studies
  \noindent  \textbf{#1}
  % at the right the duration
    \hfill 
    \framebox{% duration inside a frame box
    \parbox{9em}{%
    \centering\textbf{#2}}} \par
 % new paragraph with the school in italics
     \noindent \textit{#3} \par
     % description with no hanging and in smaller text
     \vspace*{0.5em}
     \noindent\hangindent=2em\hangafter=0 \small #4 
%back to normal size
\normalsize \par}


% work experience

\newcommand{\work}[4]{
% name of the work
  \noindent  \textbf{#1}
% at the right the duration
  \hfill 
\framebox{% duration inside a frame box
  \parbox{9em}{%
  \centering\textbf{#2}}} \par
% new paragraph with the school in italics
  \noindent \textit{#3} \par
% description with no hanging and in smaller text
  \vspace*{0.5em}
  \noindent\hangindent=2em\hangafter=0 \small #4 
%back to normal size
\normalsize \par}

\newcommand{\project}[3]{
  \noindent \textbf{#1} \par
  \noindent \textit{#2} \par
  \vspace*{0.5em}
  \noindent\hangindent=2em\hangafter=0 \small #3
  \normalsize \par
}

\titlespacing*{\section}
{0pt}{5.5ex plus 1ex minus .2ex}{4.3ex plus .2ex}
\titlespacing*{\subsection}
{0pt}{5.5ex plus 1ex minus .2ex}{4.3ex plus .2ex}

\begin{document}
% name and motto
\name{Lai, Minh Ha}
\vspace*{-13pt}
\motto{}

% personal information
\info{Email:}{laiminhha060@gmail.com}
\info{Phone:}{0963749285}
\info{Address:}{178/23 Phan Chu Trinh, Buon Ma Thuot City, Daklak province, Viet Nam}
\info{Github:}{https://github.com/zzhappyzebrazz}
\info{Linkedin:}{https://www.linkedin.com/in/minh-h\%C3\%A0-66b097177/}

% work experience
\section*{Work Experience}
\work{Viettel High Technology Industry Coperation}
{May 2023--Aug 2025}
{Software Development Engineer}
{Working on the 5G-core project, CNE (Cloud Network Exposure) team, my development work primarily focuses on the NEF (Network Exposure Function) network entity and its Northbound API services.

\begin{itemize}
    \item Analyze and break down the technical requirements in accordance with the 3GPP Release 16 of the 5G stand-alone system.
     Design and develop the following services: Procedures for Monitoring (Event Exposure) service; % \\ - Procedures for Monitoring (Event Exposure) service, which provides a mean to securely expose the information of the requested UE or group of UEs to the third-party Application Function.
     Background Data Transfer (BDT) service.
    % \\ - Background Data Transfer (BDT) service, this service enable the AF to negotiate with the system to perform  resource management of background data transfer to a set of UEs in a set of time window and usage threshold.
    \item Manage service onboarding procedures for third-party Application Function, including service provisioning; configuring the Service Level Agreement (SLA); and retrieving JWT access tokens for authentication and authorization via the OAuth2.0 framework.
    \item Configure and maintain the CI/CD pipeline for the NEF project. The pipeline includes SonarQube scans, Unit-testing, Kubernetes deployment using Helm charts, and functional testing.
    % \item Using Helm chart and Ansible to deploy the 5G core Private as a software package.
\end{itemize}}



\work{DEK Technologies VietNam}
{Nov 2021--May 2023}
{Software Engineer}
{Worked on the CSCF project, a central component in IMS architecture.
 The customer was Ericsson (Sweden), a global leader in Telecommunications.
%  \\ My responsibilities were in Product Lifecycle Management(team), my work included:

\begin{itemize}
    \item Took the role of \textbf{Security Master} in the team, ensuring that delivered software adhered to basic secure-coding standards based on the \textit{SEI CERT C++} guideline.
     Defined a Way-of-Working for the secure-coding review, addressing a gap in the process when I assumed the role.
    \item Prepared content and performed an Early System Test for the customer's Emergency Package.
    \item Investigated and resolved the trouble reports (TRs) from the customer, ensuring fixes were integrated into the integration branch alongside contributions from other feature teams.
\end{itemize}}


\work{Intel Products Vietnam}
{Aug 2020--Feb 2021}
{Engineering Intern}
{Worked in the Finish Inspection team within the Assembly Engineer department.
\begin{itemize}
    \item Took hardware and machines built by a previous intern and my mentor. 
    Monitored and troubleshot up to 30 Automated Dimensional Visual Inspection machines.
    \item Used an in-built SQL tool to access and crawl visual data from the VNAT factory database. Preprocessed the data to build a dataset for later machine learning activities.
    \item Trained and customized an Object Detection machine learning model using Python and the YOLOv3 model to identify manufacturing debris, foreign materials, and product defects on units such as Intel Comet Lake, Intel Whisky Lake, etc.
    The final demo model exceeded the target accuracy (80\%) set by my mentor.
\end{itemize}}

% education
\section*{Education}
\education{Technical University of Ilmenau (TU Ilmenau)}
{Oct 2025--Now}
{Master of Science: Communication and Signal Processing program}
{}
{}
\education{Ho Chi Minh City University of Technology (VNU-HCMUT)}
{Aug 2017--Nov 2021}
{Bachelor of Engineering: Electronic and Telecommunication; GPA: 7.29}
{}
\project{}
{Thesis project: Indoor Air Quality Monitoring system \\(Github: https://github.com/zzhappyzebrazz/IndoorAirQuality-system)}
{}

% technical skills
\section*{Technical skills}
\skill{Software Development}{\textsc{C/C++}, \textsc{Go (Golang)}, Object-Oriented Programming.}
\skill{Cloud-Native \& DevOps}{\textsc{Kubernetes, Docker, Helm, Gitlab CI/CD.}}
\skill{Telecommunications}{\textsc{3GPP Technical Specification, RFC documents, IP Multimedia Subsystem (IMS), 5Gcore network.}}

% languages
\section*{Languages}
\lan{VietNamese}{Native}
\lan{English}{IELTS Academic module overall band score: 7.5 (Test date: 22/6/2024)}
\lan{German}{Goethe-Zertifikat A2 Total result: 89/100 (Test date: 11/08/2025)}
\end{document}