\documentclass[a4paper,11pt]{letter}

% Useful packages
\usepackage[utf8]{inputenc} % For special characters
\usepackage[T1]{fontenc}    % Font encoding
\usepackage{geometry}       % To set the margins
\geometry{top=0.5cm, bottom=0cm, left=2.5cm, right=2.5cm}

\address{
    Lai Minh Ha
    \\ Phan Chu Trinh str. 179/23
    \\ Buon Ma Thuot City, Daklak province,
    \\ Vietnam
}
\date{}

% Document begins
\begin{document}
% \date{October 6, 2024}
% Recipient Information
\begin{letter}{
    Consulate General of Federal Republic of Germany
    \\ 29 Le Duan Blvd., District 1,
    \\ Ho Chi Minh City, Vietnam
}

% Add a centered headline within the letter environment
% \vspace*{-1.5cm}
% \begin{center}
%     \LARGE \textbf{Application for Master Program in Electrical Engineering}
% \end{center}

% \vspace{0.2cm} % Adds some space between the headline and the rest of the letter

% Opening salutation
\opening{\textbf{Dear Sir or Madam,}}
% Prof Dr Marc Enzmann, 
% Greeting from Vietnam,
% based in Ho Chi Minh city Vietnam 

% Introduction, teaser and Statement of Goal
My name is Lai Minh Ha, a 26-year-old software engineer from Vietnam. I'm writing to express my interest in joining your M.Sc. program in Electrical Engineering, especially Communications Technology major. I have completed a B.Eng. in Electronics and Telecommunications from Ho Chi Minh City University of Technology (VNU-HCMUT) with a GPA of 7.29/10 (German equivalent: 2.63) in November 2021, and I am now eager to advance my career by pursuing a master’s degree closely aligned with my professional expertise. 

While exploring the curriculum of the Communications Systems major, I was particularly drawn to the course \textit{Internet Security}, which I find highly relevant for students from countries like Vietnam that face significant challenges with internet fraud.The course’s OSI model-based structure offers a logical framework for understanding security protocols, aligning with best practices like Transport Layer Security (TLS) that follow similar approach. Additionally, the \textit{Machine Learning and AI} course stood out as particularly valuable. Modern mobile networks, including 5G, are increasingly integrated with cognitive network entities, such as the Network Data Analytics Function (NWDAF) and autonomous systems employing Event-Based Monitoring (EBM). I believe the course content can offer students both practical experience and an academic understanding of these cutting-edge technologies.

Beyond the program itself, studying in Germany - the technical hub of Europe, will provide me with the an opportunity to connect with world-leading telecom giants such as Deutsche Telekom, Ericsson, or Nokia. This program will not only enhance my technical expertise but also equipped me an opportunity to work for these renowned industry leaders, allowing me to participant in to cutting-edge innovations in the field. After being employed in some of those initiatives, I aim to return to Vietnam and contribute my knowledge and experience to my country's future telecommunication projects, such as 5G-advance or even 6G. This could help bridging the technological gap and also advancing our local telecom industry. 

% Through the years, I have gained a solid engineering foundation and invaluable experience from working on projects with some of the telco giants, such as Ericsson (Sweden) and Viettel (Vietnam)—the most valuable Telecoms brand in Southeast Asia. I believe this combination of academic and professional experience makes me a strong candidate for your program.

% Through my undergraduate courses, extracurricular activities, and thesis project, I have gained an extensive amount of understanding in the broad subject of electronics and telecommunications. In my third year of university, despite having a GPA of 7/10 at the time, I successfully secured a highly competitive six-month paid internship from Intel Products Vietnam. I was honored to be the only student from my program to receive this offer, which recognized my technical aptitude and potential as a promising engineer. 
% I also aced all of my university English classes, and with just three months of focused preparation alongside my full-time job, I successfully attained a C1 Advanced level in IELTS. This could be a boost for my confidence when trying to learn German as my third language.

My professional career in telecommunications as a software engineer has equipped me with valuable expertise in mobile network systems. I started my career with DEK Technologies Vietnam a vendor of Ericsson, where I gained a strong foundation in troubleshooting, technical reasoning, and effectively communicating complex technical issues to multinational colleagues—essential attributes of a competent engineer. After a year and a half contributing to the Call Session Control Function in the IMS project, I joined one of Vietnam's most important telecommunication initiatives: building the first 5G-core standalone system for Viettel, the largest mobile operator in the country. The project launched on the 20th of November 2024 and recorded nearly 3 million users after 15 days of official live.

% \vspace{0.5cm}
% Conclusion
Thank you for your consideration, and for the opportunity of applying to this program. I look forward to hearing from you soon.

% Right-aligning final information about yourself
\begin{flushright}
    Sincerely,
    \\ Lai Minh Ha
% Maria S. C.
\end{flushright}

\end{letter}

\end{document}
