\documentclass[a4paper,11pt]{letter}

% Useful packages
\usepackage[utf8]{inputenc} % For special characters
\usepackage[T1]{fontenc}    % Font encoding
\usepackage{geometry}       % To set the margins
\geometry{top=0.5cm, bottom=0cm, left=2.5cm, right=2.5cm}

\address{
    Lai, Minh Ha
    \\ Phan Chu Trinh str. 179/23
    \\ Buon Ma Thuot City, Daklak province,
    \\ Vietnam
}
\date{}

% Document begins
\begin{document}
% \date{October 6, 2024}
% Recipient Information
\begin{letter}{
    Consulate General of the Federal Republic of Germany
    \\ 33 Le Duan Blvd., District 1,
    \\ Ho Chi Minh City, Vietnam
}

% Add a centered headline within the letter environment
% \vspace*{-1.5cm}
% \begin{center}
%     \LARGE \textbf{Application for Master Program in Electrical Engineering}
% \end{center}

% \vspace{0.2cm} % Adds some space between the headline and the rest of the letter

% Opening salutation
\opening{\textbf{Dear Sir or Madam,}}

% Introduction, teaser and Statement of Goal
My name is Lai Minh Ha, a 26-year-old software engineer from Vietnam, and I have been admitted to the Master of Science program in Communication and Signal Processing at the Technical University of Ilmenau, starting in October 2025. I am writing to express my motivation and purpose for applying for a student visa to pursue my studies in Germany.

% Writing about academic background
% Professional background
% Why choosing this program and study in Germany
For my academic background, I have completed my Bachelor of Engineering degree in Electronics and Telecommunication from Vietnam National University—Ho Chi Minh City University of Technology (formerly known as Bach Khoa University) with a GPA of 7.29 (equivalent to 2.6 on the German scale). Although my GPA may not reflect my full potential, I demonstrated my capabilities during my undergraduate studies by earning a 6-month paid internship at Intel Products Vietnam as a promising engineer. At Intel, I first came into contact with real-world applications of science and the power of engineering, where engineers could turn a handful of sand (from the beach) into a technological advancement of microchips.

My experience at Intel has planted in me a dream to further explore other powers of technology in the world. After graduation, I applied to work as a software engineer and worked on the IP Multimedia Subsystem (IMS) for Ericsson, Sweden's telecom giant, once again witnessing their talented engineers build and manage a nationwide telecom system connecting millions. After a year and a half contributing to the Call Session Control Function in the IMS project, I joined one of Vietnam’s most important telecommunication initiatives: building the first 5G-core standalone system for Viettel, the largest mobile operator in the country. The project launched on the 20th of November, 2024, and recorded nearly 3 million users after 15 days of official launch.


% Future plan in Germany
% Complete the program
% Exchange student in France for AI related study
% Internship to earn experience

With a strong passion for electronics and telecommunications, the Communication and Signal Processing master program at TU Ilmenau is exactly the destination that I have been searching for. Studying in Germany—a global technology hub and a country renowned for its excellent education. What excites me even more is the program offers a unique opportunity to study at the University de Lorraine in Nancy, France, as an exchange student and advance my knowledge in Artificial Intelligence as applied to the field of communication technology and signal processing. However, I must first prove myself as an outstanding student. During my study, I also aspire to gain hands-on experience through internships at some of Europe's leading telecommunication companies, such as Deutsche Telekom, Nokia, or Ericsson. For my master's thesis, I hope to collaborate with one of those companies on cutting-edge industry research, aiming for a promising thesis defense.

% Plan to return to Vietnam
% How the degree can help
% Develop future Telecommunication generation
% ...
Upon earning myself the master's degree in Germany and invaluable working experience in Europe, I wish to come back to Vietnam and apply my knowledge in advancing the national telecommunication infrastructure, such as the development of the 5G-advanced system, the non-terrestrial communication system, or even the future of 6G. I am confident that the education I receive in Germany will equip me with the skills and experiences needed to make a significant impact in my country's Signal Processing and Communication industry.

% \vspace{0.5cm}
% Conclusion
I sincerely hope for a favorable consideration of my visa application. Thank you very much for your time and attention.

% Right-aligning final information about yourself
\begin{flushright}
    Sincerely,
    \\ Lai Minh Ha
\end{flushright}

\end{letter}

\end{document}
