\documentclass[a4paper,12pt]{letter}

% Useful packages
\usepackage[utf8]{inputenc} % For special characters
\usepackage[T1]{fontenc}    % Font encoding
\usepackage{geometry}       % To set the margins
\geometry{top=1.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm}

\address{
    Lai Minh Ha
    \\ 686/78/8 Cach Mang Thang 8
    \\ Tan Binh district, Ho Chi Minh city,
    \\ Vietnam
}
\date{}

% Document begins
\begin{document}
% \date{October 6, 2024}
% Recipient Information
\begin{letter}{
    Faculty of Electrical Engineering/Computer Science
    \\ University of Kassel
    \\ Willhelmshöher Allee 73
    \\ 34121 Kassel Germany
}

    % {Recipient Name 
    % \\ Company Name 
    % \\ Company Address 
    % \\ City 
    % \\ Country}
% Add a centered headline within the letter environment
\vspace*{-1.5cm}
\begin{center}
    \LARGE \textbf{Letter of Motivation}
\end{center}

\vspace{0.2cm} % Adds some space between the headline and the rest of the letter

% Opening salutation
\opening{Dear Faculty of Electrical Engineering/Computer Science Admission Committee,}
% Greeting from Vietnam,
% based in Ho Chi Minh city Vietnam 

% Introduction, teaser and Statement of Goal
My name is Lai Minh Ha, a software engineer with over three years of experience working on various telecommunications projects, including IP Multimedia Subsystem (IMS) and 5G-core system. I'm writing to express my interest in joining your M.Sc. program in Electrical Communication Engineering (ECE). I graduated with a B.Eng. in Electronics and Telecommunications from Ho Chi Minh City University of Technology (VNU-HCMUT) with a GPA of 7.29/10 (German equivalent: 2.63) in November 2021, and I am now eager to advance my career by pursuing a master’s degree closely aligned with my professional expertise. I have gained a solid engineering foundation and valuable experience from working on projects with some of the telco giants, such as Ericsson(Sweden) and Viettel(Vietnam)—the most valuable Telecoms brand in Southeast Asia. I believe this combination of academic and professional experience makes me a strong candidate for your program.

Throughout my undergraduate courses, extracurricular activities, and thesis project, I have gained an extensive amount of understanding in the broad subject of electronics and telecommunications. In my third year of university, despite having a GPA of 7/10 at the time, I successfully secured a highly competitive six-month paid internship from Intel Products Vietnam. Being the only student in my program to received the offer, which showed my potential as a promising engineer. I also aced all of my university English classes, and with just three months of focused preparation alongside my full-time job, I successfully attained a C1 Advanced level in IELTS. This could be a boost for my confidence when trying to learn German as my third language.

My professional career in telecommunications as a software engineer has equipped me with valuable expertise in mobile network systems. I started my career with DEK Technologies Vietnam a vendor of Ericsson, where I gained a strong foundation in troubleshooting, technical reasoning, and effectively communicating complex technical issues to multinational colleagues—essential attributes of a competent engineer. After a year and a half contributing to the Call Session Control Function in the IMS project, I joined one of Vietnam's most important telecommunication initiatives: building the first 5G-core standalone system for Viettel, the largest mobile operator in the country. The project launched on the 20th of November 2024 and recorded nearly 3 million users after 15 days of official live.

\vspace{1cm}
While exploring the program from ECE at a glance flyer, I was particularly drawn to the Wireless Communications research focus, which delves into cutting-edge technologies like 5G, 6G (the future of non-terrestrial, satellite communication). The 'Enabling Technologies for Communication Systems' section also caught my interest with its emphasis on mobile network technologies and the future of autonomous networks. In addition, the module handbook provides details about the program courses such as 'Introduction to Information Security,' which I find especially relevant for students from countries that struggle with internet fraud like Vietnam. I believe this course would provide valuable insights into European regulations like the General Data Protection Regulation (GDPR).

Beyond the ECE program itself, studying in Europe, the home of the European Telecommunication Standards Institute (ETSI), a key member of the 3GPP group that is responsible for developing Technical Specifications (TS) from 3G to 5G and 6G system, offers a unique opportunity to deepen my understanding and address the technical questions I encountered while applying these standards in real-world projects.

\vspace{1cm}
% Conclusion
Thank you for your consideration, and for the opportunity of applying to this program. I look forward to hearing from you soon.

% Right-aligning final information about yourself
\begin{flushright}
    Sincerely,
    \\ Lai Minh Ha
% Maria S. C.
\end{flushright}

\end{letter}

\end{document}
