\documentclass[a4paper,12pt]{letter}

% Useful packages
\usepackage[utf8]{inputenc} % For special characters
\usepackage[T1]{fontenc}    % Font encoding
\usepackage{geometry}       % To set the margins
\geometry{top=1.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm}

\address{
    Lai Minh Ha
    \\ 686/78/8 Cach Mang Thang 8
    \\ Tan Binh district, Ho Chi Minh city,
    \\ Vietnam
}
\date{}

% Document begins
\begin{document}
% \date{October 6, 2024}
% Recipient Information
\begin{letter}{
    Department of Electrical, Mechanical and Industrial Engineering
    \\ Anhalt University of Applied Sciences
    \\ Bernburger Str 55 
    \\ 06366 Köthen / Anhalt Germany
}

    % {Recipient Name 
    % \\ Company Name 
    % \\ Company Address 
    % \\ City 
    % \\ Country}
% Add a centered headline within the letter environment
\vspace*{-1.5cm}
\begin{center}
    \LARGE \textbf{Letter of Motivation}
\end{center}

\vspace{0.2cm} % Adds some space between the headline and the rest of the letter

% Opening salutation
\opening{Dear program Admission Committee,}
% Prof Dr Marc Enzmann, 
% Greeting from Vietnam,
% based in Ho Chi Minh city Vietnam 

% Introduction, teaser and Statement of Goal
My name is Lai Minh Ha, a software engineer with over three years of experience working on various telecommunications projects, including IP Multimedia Subsystem (IMS) and the 5G-core system. I'm writing to express my interest in joining your M.Eng. program in Electrical and Computer Engineering Communication Engineering, especially hte Communication Systems major. I have completed a B.Eng. in Electronics - Telecommunications from Ho Chi Minh City University of Technology (VNU-HCMUT) with a GPA of 7.29/10 (German equivalent: 2.63) in November 2021, and I am now eager to advance my career by pursuing a master's degree closely aligned with my professional expertise. 
Through the years, I have gained a solid engineering foundation and invaluable experience from working on projects with some of the telco giants, such as Ericsson(Sweden) and Viettel(Vietnam)—the most valuable Telecoms brand in Southeast Asia. I believe this combination of academic and professional experience makes me a strong candidate for your program.

% Talk about my unique qualification, experience working in the Telco company such as Ericsson, Viettel
% 

% Body of the letter is about knowledge and skills (in bachelor degree?) or relevant professional experience, other relevant skills
% Begin with a topic sentence
% make sure to mention previous degree and courses e.g. academic performance, major & specializations projects
% relevant work experience: internship, trainings
% further important skill: language, computer
% Stick to the order: education -> work experience -> skills
% Do not skip over your educational background too quickly
% Qualifications
Through my undergraduate courses, extracurricular activities, and thesis project, I have gained an extensive amount of understanding in the broad subject of electronics and telecommunications. In my third year of university, despite having a GPA of 7/10 at the time, I successfully secured a highly competitive six-month paid internship from Intel Products Vietnam. I was honored to be the only student from my program to receive this offer, which recognized my technical aptitude and potential as a promising engineer. I also aced all of my university English classes, and with just three months of focused preparation alongside my full-time job, I successfully attained a C1 Advanced level in IELTS. This could be a boost for my confidence when trying to learn German as my third language.
% In my third year internship, with only a GPA of 7/10 at the time, I was able to convince the recruiter from Intel Products Vietnam that I am a promising engineer and I was the only student from my program to received an offer of a 6-month paid internship.
%  During my internship, I learned how a modern CPU is manufactured, and finished my internship with a Machine learning project which can detect debris or foreign materials on CPU unit with the model confidence was above 80\% for each prediction. 
 % Talk about how I obtain the IELTS certificate in a 3 months self study while on my job
  % and express that I could extend my language learning ability by try hard in German, and received a A2 CERT and then got a B1 after study in German

My professional career in telecommunications as a software engineer has equipped me with valuable expertise in mobile network systems. I started my career with DEK Technologies Vietnam a vendor of Ericsson, where I gained a strong foundation in troubleshooting, technical reasoning, and effectively communicating complex technical issues to multinational colleagues—essential attributes of a competent engineer. After a year and a half contributing to the Call Session Control Function in the IMS project, I joined one of Vietnam's most important telecommunication initiatives: building the first 5G-core standalone system for Viettel, the largest mobile operator in the country. The project launched on the 20th of November 2024 and recorded nearly 3 million users after 15 days of official live.



% Not to mention, the most important is my current professional occupation in telecommunication field of mobile network system. I started my career with a strong foundation from an Ericsson project that built a solid background in engineering. The process of troubleshooting, engineering reasoning and also how to express the difficult technical problem to other colleagues is as important as a competent engineer. After a year and a half working on the Core Session Control Function in IMS project, I go on and join one of the most important Telecommunication project in my country, building the first 5G-core stand alone system for Viettel, the largest mobile operator in Vietnam. The project on-air on the 20th of November 2024, serving more than 3 million user on its initiative.

% Why this program?
% Justify your choice of programme
% Why your qualifications, experiences and competencies make you an ideal fit for this programme
% Why this program is uniquely suited to help you in the pursuit of your professional and/or personal goals.
% Mention specific program details that interest you: particular modules, research, exchange opportunities, internship & industry partnership opportunities
% Part 1 is why you are a good fit for the program
% part 2 what the program can do for you
% what it helps you to accomplished 
% getting your dream job, field of work, specific knowledge
\vspace{1cm}
While exploring the curriculum of the Communications Systems major, I was particularly drawn to the course \textit{Internet Security}, which I find highly relevant for students from countries like Vietnam that face significant challenges with internet fraud.The course’s OSI model-based structure offers a logical framework for understanding security protocols, aligning with best practices like Transport Layer Security (TLS) that follow similar approach. Additionally, the \textit{Machine Learning and AI} course stood out as particularly valuable. Modern mobile networks, including 5G, are increasingly integrated with cognitive network entities, such as the Network Data Analytics Function (NWDAF) and autonomous systems employing Event-Based Monitoring (EBM). I believe the course content can offer students both practical experience and an academic understanding of these cutting-edge technologies.

% For the rising queries regarding of the ECE program, from the flyer of the ECE at glance, it caught my attention on the Wireless Communication research which mention about the latest mobile connectivity such as 5G, 6G and potential non-terrestrial (satellite) communication. Also the Enabling Technologies for Communication Systems section which depict Mobile Network technology or the future of autonomous network. The module handbook also going to detail about some of the courses such as Introduction to Information Security, which I found extremely useful for student from country with the infamous of internet fraud like Vietnam to understand and study some of the regulation from European such as the General Data Protection Regulation (GDPR).

Beyond the program itself, studying in Europe, the home of the European Telecommunication Standards Institute (ETSI), a key member of the 3GPP group that is responsible for developing Technical Specifications (TS) from 3G to 5G and 6G system, offers a unique opportunity to deepen my understanding and address the technical questions I encountered while applying these standards in real-world projects.
%during my work-related while analyzing and implementing these standards.
% For the last mention, an invitation to play this game of life, to see how far I could go, to you how youth turn out to be.

%Beyond the ECE program itself, studying in Germany—the home of the European Telecommunication Standards Institute (ETSI), a key member of the 3GPP group responsible for developing technical specifications from 3G to 5G and beyond—offers a unique opportunity to deepen my understanding of these standards. This environment would allow me to address the technical questions I encountered during my career while analyzing and implementing these specifications, especially as the industry moves toward 6G technologies.
\vspace{1cm}
% Conclusion
Thank you for your consideration, and for the opportunity of applying to this program. I look forward to hearing from you soon.

% Closing salutation
% \closing{Sincerely,
% \\ Maria S. C.
% }

% Right-aligning final information about yourself
\begin{flushright}
    Sincerely,
    \\ Lai Minh Ha
% Maria S. C.
\end{flushright}

\end{letter}

\end{document}
