\documentclass[a4paper,12pt]{letter}

% Useful packages
\usepackage[utf8]{inputenc} % For special characters
\usepackage[T1]{fontenc}    % Font encoding
\usepackage{geometry}       % To set the margins
\geometry{top=1cm, bottom=0.5cm, left=2.5cm, right=2.5cm}

\address{
    Lai Minh Ha
    \\ 686/78/8 Cach Mang Thang 8
    \\ Tan Binh district, Ho Chi Minh city,
    \\ Vietnam
}
\date{}

% Document begins
\begin{document}
% \date{October 6, 2024}
% Recipient Information
\begin{letter}{
    Faculty of Electrical Engineering/Computer Science
    \\ University of Kassel
    \\ Willhelmshöher Allee 73
    \\ 34121 Kassel Germany
}

    % {Recipient Name 
    % \\ Company Name 
    % \\ Company Address 
    % \\ City 
    % \\ Country}
% Add a centered headline within the letter environment
\vspace*{-1.5cm}
\begin{center}
    \LARGE \textbf{Letter of Motivation}
\end{center}

\vspace{0.2cm} % Adds some space between the headline and the rest of the letter

% Opening salutation
\opening{Dear Dr.Ing. Nour Mansour,}

% Introduction, teaser and Statement of Goal
My name is Lai Minh Ha, a software engineer from Vietnam with more than 3 years working on various Telecommunication projects such as IMS (Ip Multimedia Subsystem), 5G-core system, and I am writing to express my interest in joining your M.Sc. program in Electrical Communication Engineering (ECE) program. I have completed my B.Eng. in Electronics -Telecommunications from Ho Chi Minh city University of Technology (VNU-HCMUT) with a GPA of 7.29/10 (German equivalent: 2.63) in November of 2021, and am now looking to take the next step to advance in my career with a master's degree closely related to my professional experience. I believe my solid background gathered through out the years and precious experience from the projects I worked on from some of world giant in the telecommunication such as Ericsson from Sweden, or Viettel (the most valuable Telecoms brand in Southeast Asia) from my home country, makes me a strong candidate for this program. 

% Talk about my unique qualification, experience working in the Telco company such as Ericsson, Viettel
% 

% Body of the letter is about knowledge and skills (in bachelor degree?) or relevant professional experience, other relevant skills
% Begin with a topic sentence
% make sure to mention previous degree and courses e.g. academic performance, major & specializations projects
% relevant work experience: internship, trainings
% further important skill: language, computer
% Stick to the order: education -> work experience -> skills
% Do not skip over your educational background too quickly
% Qualifications
I have through my undergraduate courses, extracurricular activities, thesis project gathered extensive knowledge in the vast field of electronics and telecommunications. I was also the only student in my program to earn a 6-month internship with allowance from Intel Products Vietnam, that with just a GPA of 7/10 at that time and I can convince the recruiter that a promising and competence engineer. During my internship, I learned how a modern CPU is manufactured, and finished my internship with a Machine learning project which can detect debris or foreign materials on CPU unit. 
 % Talk about how I obtain the IELTS certificate in a 3 months self study while on my job
 % and express that I could extend my language learning ability by try hard in German, and received a A2 CERT and then got a B1 after study in German
Although my  I also made sure to take all available courses in English in order to refine my technical vocabulary and ensure that language will be no barrier in my English-taught graduate courses.

% Why this program?
% Justify your choice of programme
% Why your qualifications, experiences and competencies make you an ideal fit for this programme
% Why this program is uniquely suited to help you in the pursuit of your professional and/or personal goals.
% Mention specific program details that interest you: particular modules, research, exchange opportunities, internship & industry partnership opportunities
% Part 1 is why you are a good fit for the program
% part 2 what the program can do for you
% what it helps you to accomplished 
% getting your dream job, field of work, specific knowledge
What makes RWTH's Automotive Engineering program particularly appealing to me is the fact that its modules strike a brilliant balance between practice and theory. This M.Sc. program will contribute greatly to my expertise in the field, significantly strengthening my grasp of the subject. I would particularly look forward to taking the courses "Structural Design of Vehicles" (which would build upon my internship experience while adding a new angle through its focus on passive safety), and "Environmental Sustainability in Transport Engineering" (providing a deeper look into Mr.Backes' and my own area of interest, optimizing energy management). These courses, among others, would help me build a solid foundation for a future career in eco-friendly and forward-thinking automobile manufacturing. With the above qualifications and experiences, I believe that I am a strong candidate for this program, and that this M.Sc. program will propel me towards my goal.

A master programme from the home of European Telecommunication Standards Institute (ETSI) a member of the 3GPP group that in charge of the Technical Specification (TS) of all the Telecommunication Generation from 3G up to 5G, and 6G in a close future, could help me have a deeper understanding of the those specifications.
also to unwind the questions I have during my working time
\\
% Conclusion
Thank you for your consideration, and for the opportunity of applying to this program. I look forward to hearing from you soon.

% Closing salutation
% \closing{Sincerely,
% \\ Maria S. C.
% }

% Right-aligning final information about yourself
\begin{flushright}
    Sincerely,
    \\ Lai Minh Ha
% Maria S. C.
\end{flushright}

\end{letter}

\end{document}
