\documentclass[10pt]{article}

%% PACKAGES %%

\usepackage[english]{babel} % multilingual support
\usepackage[utf8x]{inputenc} % encoding
\usepackage{blindtext} % to insert blind text
\usepackage{hyperref}
\usepackage[compact]{titlesec}         % you need this package

% Set the default font
\usepackage{tgpagella}

% set the page layout
\usepackage{geometry}
\geometry{
  a4paper,
  left=5mm,
  right=5mm,
  bottom=3mm,
  top=4mm}

% empty the headers, footers, page numbers…
\pagestyle{empty}

% Custom sectioning with secsty
\usepackage{sectsty}

\sectionfont{%                        
    \large % make sections smaller
    \fontfamily{qag}\selectfont % change font family
    \sectionrule{0pt}{0pt}{-5pt}{1pt} % insert a thin rule
}

\titlespacing{\section}{0pt}{0pt}{0pt}

%% MACROS %%

% size of the boxes used to align text
\newlength{\spacebox}
\settowidth{\spacebox}{123456789}

% vertical space separator between entries
\newcommand{\sepspace}{\vspace*{0.1em}}

% name
\newcommand{\name}[1]{
\Huge % font size
\fontfamily{phv}\selectfont % font family
% print name centered and bold
\begin{center} \textbf{#1} \end{center}\par
% back to normal size and font
\normalsize\normalfont}

% motto
\newcommand{\motto}[1]{
  \large % font size
  \fontfamily{phv}\selectfont % font family
% print motto centered and slanted
  \begin{center} \textsl{#1}\end{center}\par
% back to normal size and font
  \normalsize \normalfont}


% personal information
\newcommand{\info}[2]{
% set specific indentation for personal information
  \noindent\hangindent=0em\hangafter=0
% create a box to align two pieces of text
  \parbox{\spacebox}{%
  \textit{#1}} % slanted entry name
  #2 \par} % entry value


% skill
\newcommand{\skill}[2]{
% set specific indentation for personal information
\noindent\hangindent=0em\hangafter=0
% create a box to align two pieces of text
\parbox{3\spacebox}{% three times larger box
\textsc{#1}} % small caps entry name
#2 \par} % entry value

% language level
\newcommand{\lan}[2]{
    % set specific indentation for personal information
    \noindent\hangindent=0em\hangafter=0
    % create a box to align two pieces of text
    \parbox{3\spacebox}{%
        \textbf{#1}} % bold font entry name
     #2 \par}    % entry value

% education entry
\newcommand{\education}[4]{

% name of the studies
  \noindent  \textbf{#1}
  % at the right the duration
    \hfill 
    \framebox{% duration inside a frame box
    \parbox{9em}{%
    \centering\textbf{#2}}} \par
 % new paragraph with the school in italics
     \noindent \textit{#3} \par
     % description with no hanging and in smaller text
     \vspace*{0.5em}
     \noindent\hangindent=2em\hangafter=0 \small #4 
%back to normal size
\normalsize \par}


% work experience

\newcommand{\work}[4]{
% name of the work
  \noindent  \textbf{#1}
% at the right the duration
  \hfill 
\framebox{% duration inside a frame box
  \parbox{9em}{%
  \centering\textbf{#2}}} \par
% new paragraph with the school in italics
  \noindent \textit{#3} \par
% description with no hanging and in smaller text
  \vspace*{0.5em}
  \noindent\hangindent=2em\hangafter=0 \small #4 
%back to normal size
\normalsize \par}

\newcommand{\project}[3]{
  \noindent \textbf{#1} \par
  \noindent \textit{#2} \par
  \vspace*{0.5em}
  \noindent\hangindent=2em\hangafter=0 \small #3
  \normalsize \par
}

\titlespacing*{\section}
{0pt}{5.5ex plus 1ex minus .2ex}{4.3ex plus .2ex}
\titlespacing*{\subsection}
{0pt}{5.5ex plus 1ex minus .2ex}{4.3ex plus .2ex}

\begin{document}
% name and motto
\name{Lai Minh Ha}
\vspace*{-13pt}
\motto{}

% personal information
\info{Email:}{laiminhha060@gmail.com}
\info{Phone:}{0963749285}
\info{Address:}{686/78/8 Cach Mang Thang 8, Tan Binh, Ho Chi Minh city}
\info{Github:}{https://github.com/zzhappyzebrazz}
\info{Linkedin:}{https://www.linkedin.com/in/minh-h\%C3\%A0-66b097177/}

% work experience
\section*{Work Experience}
\work{Viettel High Technology Industry Coperation}
{May 2023--Now}
{Software Development Engineer}
{Working on 5G core project, MEC (Multi-access Edge Computing) team, my development work primarily focuses on the NEF (Network Exposure Function) network entity and its Northbound API services.

\begin{itemize}
    \item Breakdown and analyze the technical requirements in accordance with the 3GPP Release 16 of 5G stand-alone system.
    \\ Design and develop the following services:
    \\ - Procedures for Monitoring (Event Exposure) service.
    % \\ - Procedures for Monitoring (Event Exposure) service, which provides a mean to securely expose the information of the requested UE or group of UEs to the third-party Application Function.
    \\ - Background Data Transfer (BDT) service.
    % \\ - Background Data Transfer (BDT) service, this service enable the AF to negotiate with the system to perform  resource management of background data transfer to a set of UEs in a set of time window and usage threshold.
    \item Handle the service onboarding procedures for third-party Application Function, include: service provisioning; configuring the Service Level Agreement (SLA); retrieving JWT access token for authentication, authorization through the OAuth2.0 framework.
    \item Config and Maintain CICD pipeline for the NEF project. The pipeline includes SonarQube scan, unit testing, Kubernetes deployment and functional testing.
    \item Using Helm chart and Ansible to deploy the 5G core Private as a software package.
\end{itemize}}



\work{DEK Technologies VietNam}
{Nov 2021--May 2023}
{Software Engineer}
{Worked on the CSCF project, a central component in IMS architecture.
 My customer is Ericsson from Sweden, one of the world's leading companies in telecommunications.
 \\ My responsibilities are in Product Lifecycle Management(team), my work included:

\begin{itemize}
    \item Took the role of Security Master in my team, ensured the delivered software meets the basic secure-coding standard.
     The Standards(Rules) are based on the SEI CERT C++ book. 
     Defined a Way-of-Working for secure-coding review, which was omitted at the time I took over. 
    \item Prepared content and perform early System Test for customer's Emergency Package.
    \item Resolved the Trouble Reports from customer, the remediation then delivered into the integration branch along with other feature teams.
\end{itemize}}


\work{Intel Products Vietnam}
{Aug 2020--Feb 2021}
{Engineering Intern}
{Worked in the Finish Inspection team, Assembly Engineer department. My work included:
\begin{itemize}
    \item Inherited the hardwares and machines built from a prior intern and my mentor. 
    Tracked and and troubleshot those Automated Dimensional Visual Inspection(upto 30) machines.
    \item Used an in-build SQL tool to access and crawled data from VNAT factory. 
    With the provided data, I performed data pre-processing and built a data set for further machine learning activities. 
    \item Trained and customized an Object Detection(Python, YOLOv3) model to detect faulty manufacturing, foreign materials and defects on unit product such as Intel Comet Lake, Intel Whisky Lake, ect...
    The final demo model exceeded the target Accuracy(80\%) set by my mentor.
\end{itemize}}

% education
\section*{Education}
\education{Ho Chi Minh City University of Technology (HCMUT)}
{Aug 2017--Nov 2021}
{Bachelor of Engineering: Electronic and Telecommunication; GPA: 7.29}
{}
\project{}
{Thesis project: Indoor Air Quality Monitoring system}
{
  \begin{itemize}
    \item Fully designed and crafted IOT devices that embedded with ARM Cortex-M0 MCU. 
     Those devices are solely for the attention of collecting PM2.5 fine dust and many other Volatile Organic Compounds(VOC) concentrations. 
     The data is packed and sent to a web server (a Raspberry Pie) via MQTT protocol for analysis and visualization(achieved a grade of 89\%).

    \item Github: https://github.com/zzhappyzebrazz/IndoorAirQuality-system
  \end{itemize}
}
{}

% technical skills
\section*{Technical skills}
\skill{Programming languages}{\textsc{C/C++}, \textsc{Golang}.}
\skill{Cloud Native}{\textsc{Kubernetes, Docker, Helm chart, CI/CD with Gitlab.}}
\skill{Technical document}{\textsc{3GPP Technical Specification, RFC documents, Design and Guideline documentation.}}
\skill{Other}{\textsc{Git, Linux, OOP, Troubleshooting.}}

% languages
\section*{Languages}
\lan{VietNamese}{Native}
\lan{English}{IELTS Academic module overall band score: 7.5 (Test date: 22/6/2024)

\hspace{4.2cm} TOEIC Listening and Reading 950/990 (Test date: 06/12/2020)}
\end{document}